### 2015-02-07 paper_40_mpi.tex
fix some more minor typos
adding MPI overview in chapter 4

Software development organizations struggle to measure overall performance.  The Master Performance Indicator (MPI) is an algorithm to provide a single number score for the performance of a software development organization. It works by statistically analyzing the past performance of the organization and using that information to score an organization on current and future performance.  MPI focuses on the following elements of a software development organization: \textit{requirements},  \textit{quality},  \textit{on-schedule},  \textit{availability}, and  \textit{satisfaction}. MPI is not meant to be comparative between organizations, but to measure the amount of increase or decrease a single organization exhibits.
It is possible the concept could be expanded beyond just software development organizations or the previously stated elements.

@@

            As long as those 5 features are met, the range can be anything.  The range of $[-1,1]$ was chosen because it is easy to scale to a different range such as $[-10,10]$ or $[-100,100]$.  It maybe makes sense to use variables for the range.  The formulas are designed to fall in the range $[-1,1]$.  Thus scaling can be applied to obtain values in any appropriate range.

@@

\caption{3 IMPORTANT QUESTIONS FOR SOFTWARE ANALYTICS AND MPI}
\label{tab:questions}
\end{longtable}

>>>>

Software development organizations struggle to measure overall performance.  
        The Master Performance Indicator (MPI) is an algorithm to provide a single 
        number score to measure the performance of a software development organization. 
        It works by statistically analyzing the past performance of the 
        organization and using that information to score an organization 
        on current performance.  MPI focuses on the following 
        elements of a software development organization: \textit{quality}, 
        \textit{availability}, \textit{satisfaction}, \textit{schedule},
        and \textit{requirements}. A separate MPI
        score is calculated for each element and 
        then aggregated together to form an overall 
        MPI score.   \textbf{MPI is not meant to be comparative between
        organizations, but to measure the amount of increase or decrease
        a single organization exhibits across elements}.  MPI is made to be easily 
        expandable to other elements if desired.

        The scores for MPI will range from -100, indicating the worst 
        performance, all the way to +100, indicating perfection.
        A score of 0 is an indication of meeting the basic expectations. 
        A negative score indicates under-performance and a 
        positive score indicates over-performance.   Here are some 
        examples. An MPI score of 35 means the organization is 
        performing 35\% better than expected.  Conversely, a score 
        of -15 means an organization is performing 15\% worse than expected.

@@

            As long as those 5 features are met, the range can be anything.  The range of $[-100,100]$ was chosen because it is easy to scale to a different range such as $[-10,10]$ or $[-1,1]$.  It maybe makes sense to use variables for the range.  The formulas are designed to fall in the range $[-100,100]$.  Thus scaling can be applied to obtain values in any appropriate range.

@@

\caption{IMPORTANT QUESTIONS FOR SOFTWARE ANALYTICS AND MPI}
\label{tab:questions}
\end{longtable}
